### 2018-06-08 Writing/response_to_reviewers.tex

\begin{enumerate}
\item{\textcolor{blue}{Distinctiveness}}
\item{\textcolor{blue}{Non-negativity}}
\item{\textcolor{blue}{Symmetry}}
\item{\textcolor{blue}{Triangle inequality}}
\item{\textcolor{blue}{Four-point condition}}
\end{enumerate}

\item{\textcolor{blue}{If so, then it is actually an evolutionary distance, and it can be used as such; if not, then it is another type of distance. Establishing the type of distance may be overkill, but the characterization of a metric helps to determine what it can be used for, and what it cannot be used for.}}

In the supplementary materials 1, we mathematically define the characteristics of $CD$ and proved that it is a distance metric since it respects the four first points:

\begin{enumerate}
\item Distinctiveness: $CD_{(x,y)} = 0 \Leftrightarrow x = y$, proved in equation 11 (note that we corrected the error highlighted by reviewer 2 with a more restrictive definition of $x$ and $y$).
\item Non-negativity: $CD_{(x,y)} \geq 0$, proved in equation 10.
\item Symmetry: $CD_{x,y} = CD_{y,x}$, proved in equation 12.
\item Triangle inequality: $CD_{(x,y)} \leq CD_{(x,z)} + CD_{(z,y)}$, proved in equation 13.
\item Four point condition: $CD_{(i,j)} + CD_{(m,n)} \leq \text{max}{(CD_{(i,m)} + CD_{(j,n)} ; CD_{(j,m)} + CD_{(i,n)} )}$, proved in equation 15.
\end{enumerate}

### 2018-06-08 Writing/supplementary/Sup1-CharDiff.tex
Added four point proof

\texttt{x' = {1,1,2,2,3,3}} and \texttt{y' = {1,2,2,2,3,3}}

\indent The following proofs consider that the \textit{xyz} notation was applied.

@@

@@

>>>>

\texttt{x' = {1,1,2,2,3,3}} and \texttt{y' = {1,1,2,2,3,3}}

\noindent The following proofs consider that the \textit{xyz} notation was applied.

@@

\noindent Furthermore, $CD$ is a evolutionary distance metric if it satisfies the four point condition:

\begin{equation}
    \label{fourpoint}
    CD_{(i,j)} + CD_{(m,n)} \leq \text{max}{(CD_{(i,m)} + CD_{(j,n)} ; CD_{(j,m)} + CD_{(i,n)} )}
\end{equation}

@@

\subsection{Four point condition}

For any $n \in [1;\infty)$ and any four distinct characters $i$, $j$, $n$ and $m$, and if equations \ref{Positivity} and \ref{Subadditivity} are true, the pairwise distances $CD_{(i,j)}$, $CD_{(m,n)}$, $CD_{(i,m)}$, $CD_{(j,n)}$, $CD_{(j,m)}$ and $CD_{(i,n)}$ can be represented as a combination of any five values $a$, $b$, $c$, $d$ and $e$ $\geq 0$:

\begin{figure}[!htbp]
\centering
   \includegraphics[width=0.5\textwidth]{Four_point.pdf}
\end{figure}

Then:

\begin{equation}
    \begin{aligned}
    CD_{(i,j)} = a + b \\
    CD_{(m,n)} = d + e \\
    CD_{(i,m)} = a + c + d \\
    CD_{(j,n)} = b + c + e \\
    CD_{(j,m)} = b + c + d \\
    CD_{(i,n)} = a + c + e \\
    \end{aligned}
\end{equation}

Thus:

\begin{equation}
    \begin{gathered}
    CD_{(i,j)} + CD_{(m,n)} \leq \text{max}{(CD_{(i,m)} + CD_{(j,n)} ; CD_{(j,m)} + CD_{(i,n)} )} \\ 
    a + b + d + e \leq \text{max} (a+c+d+b+c+e; b+c+d+a+c+e) \\
    a + b + d + e \leq a+b+2c+e+d \\
    2c \geq 0 \\
    \end{gathered}
\end{equation}

Thus equation \ref{fourpoint} is true.
